---
title: "Integrative analysis"
author: ""
output: github_document
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Integrative analysis}
  %\usepackage[utf8]{inputenc}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  eval=TRUE,
  comment = "#>"
)
```

## Loading datasets
Each dataset represents one batch and must be a `SingleCellExperiment` object. The objects are are merged by passing a list in the next step.
```{r,warning=FALSE,message=FALSE}

library(dropClust)
load(url("https://raw.githubusercontent.com/LuyiTian/CellBench_data/master/data/sincell_with_class.RData"))

objects = list()

objects[[1]] = sce_sc_10x_qc

objects[[2]] = sce_sc_CELseq2_qc

objects[[3]] = sce_sc_Dropseq_qc

```

## Merge datasets using dropClust
Datasets can be merged in two ways: using a set of DE genes from each batch or, using the union of the sets of highly variable genes from each batch.

```{r, echo=FALSE}

all.objects = objects
merged_data<-Merge(all.objects)

```


## Perform correction and dimension reduction

```{r}
set.seed(1)
dc.corr <-  Correction(merged_data,  method="default", close_th = 0.1, cells_th = 0.1,
                       components = 10, n_neighbors = 20,  min_dist = 0.5)
```

## Perform Clustering on integrated dimensions

```{r}
dc.corr = Cluster(dc.corr,method = "kmeans",centers = 3)
```
## Visualizing clusters

Compute 2D embeddings for samples followed by post-hoc clustering.

```{r, fig.asp=1, fig.cap="Batch corrected dropClust based Clustering."}
ScatterPlot(dc.corr, title = "Clusters")

```
## Optional Batch correction
Users can use `fastmnn` method for batch correction. Specific arguments of fastmnn can also be passed through the `Correction` module.
```{r, message=FALSE, warning=FALSE}
merged_data.fastmnn<-Merge(all.objects,use.de.genes = FALSE)

set.seed(1)
mnn.corr <-  Correction(merged_data.fastmnn,  method="fastmnn", d = 10)

mnn.corr = Cluster(mnn.corr,method = "kmeans",centers = 3)

ScatterPlot(mnn.corr, title = "Clusters")

```

## Marker discovery from the merged dataset
```{r}
de<-FindMarkers(dc.corr,q_th = 0.001, lfc_th = 1.2,nDE = 10)
de$genes.df
```
